Many Analystis Project

### 2021-10-05 analysis.Rmd
Update analysis.Rmd
updated graphs + simulation

# libraries
# libraries and settings
library("tidyverse")
library("easystats")
library("ggplot2") #plots
library("sjstats") #test statistics
library("sjPlot")
library("sjmisc")
library("insight")
library("see")
library("performance")
library("ggraph")
library("parameters")
library("lme4")
library("psych") ## correlation matrix
library("table1")
library("ggeffects")
library("gghighlight")
#library("naniar") # missingness
#library("Amelia")
#library("magrittr")
library("patchwork")
library("texreg")
library("viridis")
library("ggpubr")
library("ggsci") 
library("here")
library("citr")
library("rethinking")
#library("statsExpressions")
library("ggstatsplot")
library("ggthemes")
library("ggdag")
library("papaja")
library("rstan")
library("brms")
library("tidybayes")
library("bayesplot")
library("dagitty")
library("ggdag")
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
```

@@

d0 <-ggdag::ggdag(dg1, text = FALSE, use_labels = "label")  + theme_dag() + ggtitle("Assumed Causal Relations")
# graph adjustment sets

d1<-ggdag::ggdag_adjustment_set(dg1, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment sets for Belief in God")

d1
```

@@

ggdag::ggdag(dg2, text = FALSE, use_labels = "label")  + theme_dag()
# graph adjustment sets
d2<-ggdag::ggdag_adjustment_set(dg2, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment set for Religious Service")

d2
```

@@

```{r}
library(patchwork)
( (d0)/(d1 + d2) +   plot_layout(guides = 'collect'))  +((d0a) + (d1a)) + plot_annotation(title = 'If distressing life events affect religious belief and behaviour, longtidinal data are needed for causal inference', tag_levels = "a")
# 14/12
```

@@

```{r}
library(patchwork)

@@

## Results summary Belief ~ Anxiety

@@

```{r}
parF1 <- parameters::model_parameters(m1 ) 
plot(parF1,  sort = TRUE) +theme_lucid() #option -->
```

@@

```{r}
parR1<-parameters::model_parameters(m1,effects = "random" ) 
plot(parR1,  sort = TRUE) +theme_lucid() #option -->
```

@@

plot(p0, plot = FALSE)[[1]]   + xlab("bg_s") + ylab ("anxiety 1-5") +
  labs(title = "Predicted effects of bg_s")
```

@@

```{r}
parF<-parameters::model_parameters(m2 ) 
plot(parF,  sort = TRUE) +theme_lucid() #option -->
```

@@

```{r}
parR<-parameters::model_parameters(m2,effects = "random" ) 
plot(parR,  sort = TRUE) +theme_lucid() #option -->
```

@@

plot(p0b, plot = FALSE)[[1]]   + xlab("ch_s") + ylab ("anxiety 1-5") +
  labs(title = "Predicted effects of ch_s")
```

@@

>>>>

# libraries
# libraries and settings
library("tidyverse")
library("easystats")
library("ggplot2") #plots
library("sjstats") #test statistics
library("sjPlot")
library("sjmisc")
library("insight")
library("see")
library("performance")
library("ggraph")
library("parameters")
library("lme4")
library("psych") ## correlation matrix
library("table1")
library("ggeffects")
library("gghighlight")
library("texreg")
library("kableExtra")
#library("naniar") # missingness
#library("Amelia")
#library("magrittr")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
#library("rethinking")
#library("statsExpressions")
#library("ggstatsplot")
library("ggthemes")
library("ggdag")
#library("papaja")
library("rstan")
library("brms")
library("tidybayes")
library("bayesplot")
library("dagitty")
library("ggdag")
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
```

@@

dp0 <-ggdag::ggdag(dg1, text = FALSE, use_labels = "label")  + theme_dag() + ggtitle("Assumed Causal Relations")
# graph adjustment sets

dp1<-ggdag::ggdag_adjustment_set(dg1, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment sets for Belief in God")

#dp1
```

@@

ggdag::ggdag(dg2, text = FALSE, use_labels = "label")  + theme_dag()
# graph adjustment sets
dp2<-ggdag::ggdag_adjustment_set(dg2, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment set for Religious Service")

#dp2
```

@@

```{r}
library(patchwork)
( (dp0)/(dp1 + dp2) +   plot_layout(guides = 'collect'))  +((d0a) + (d1a)) + plot_annotation(title = 'If distressing life events affect religious belief and behaviour, longtidinal data are needed for causal inference', tag_levels = "a")
# 14/12
```

```{r}
library(lme4)

@@

```{r}
library(patchwork)
m0 <- lmer(
    anx ~
    bg_s +
  #  ch_s +
    age_s  +
    male +
    ( bg_s | country), 
  data = d1)

sjPlot::tab_model(m0)

m0 <- brm(
  anx ~
    bg_s +
    #ch_s +
    age_s  +
    male +
    (1 + bg_s | country),
  data = d1,
  family = cumulative(link = "logit"),
  seed = 1234,
  warmup = 1000,
  iter = 3000,
  chains = 4,
  file = here::here("models", "m2o_real")
)

@@

## Results summary Anxiety ~ Belief

@@

```{r}
parF1 <- parameters::model_parameters(m1 ) 
parF1
plot(parF1,  sort = TRUE) +theme_lucid() #option -->
```

@@

```{r}
parR1<-parameters::model_parameters(m1,effects = "random" ) 
belief_random <- plot(parR1,  sort = TRUE) +theme_lucid()  + labs(title = "Country level heterogeneity in belief (co)-variances: India is an outlier.") 
```

@@

belief_fixed <- plot(p0, plot = FALSE)[[1]]   + xlab("belief (standardised)") + ylab ("anxiety (ordinal 1-5)") +
  labs(title = "Increasing belief predicts increasing anxiety")
```

@@

```{r}
parc<-parameters::model_parameters(m2 ) 
plot(parc,  sort = TRUE) + theme_lucid() #option -->
```

@@

```{r}
parcR<-parameters::model_parameters(m2,effects = "random" ) 
church_random <- plot(parcR,  sort = TRUE) +theme_lucid() + labs(title = "Country level heterogeneity in religious service (co)-variances: India is again an outlier.") #option -->
```

@@

church_fixed <-plot(p0b, plot = FALSE)[[1]]  + xlab("religious service attendance (standardised)") + ylab ("anxiety (ordinal 1-5)") +
  labs(title = "Increasing religious service attendence predicts lower anxiety.")

church_fixed
```

Combined plot

```{r}
(belief_fixed + church_fixed )/( belief_random + church_random  ) +
  plot_annotation(tag_levels = "a") + plot_layout(guides = "collect")

# coef_graph 15 x 15 
```

@@

## Tables

### Anxiety ~ Belief

```{r}
library(kableExtra)
parameters::parameters(
  m1,
  test = "pd",
  priors = FALSE, 
  effects = "all",
  drop = TRUE,
  group_level = FALSE,
  diagnostic = "Rhat") %>%
    mutate_if(is.numeric, ~ round(., 2)) %>%
    mutate_all(funs(str_replace(., "b_", ""))) %>%
    kable(booktabs = T, "latex", caption =  "Belief in God is positively related to anxiety") %>%
    print()
```

### Anxiety ~ Chruch
```{r}
library(kableExtra)
parameters::parameters(
  m2,
  test = "pd",
  priors = FALSE, 
  effects = "all",
  drop = TRUE,
  group_level = FALSE,
  diagnostic = "Rhat") %>%
    mutate_if(is.numeric, ~ round(., 2)) %>%
    mutate_all(funs(str_replace(., "b_", ""))) %>%
    kable(booktabs = T, "latex", caption =  "Religious Service is negatively related to anxiety") %>%
    print()
```

## Simulation

```{r}
set.seed(123)
n <- 1000
U <- rnorm( n ) # distressing events (unmeasured)
C <- rnorm( n, U ) # religious service attendance, increase with distress
B <- rnorm( n , C + U ) )# belief increase with service + distressing events
Y <- rnorm( n , U - C ) # measured distress caused by distress, reduced by church attendance.

# simulate data
simdat <- data.frame(
  Belief = B, # belief
  ReligiousService = C, # religious service
  U = U, # distressing events (unmeasured)
  Anxiety = Y  # outcome
  )

# summarise results
summary(
  mod1 <- lm(Anxiety ~ Belief + ReligiousService, data = simdat)
)
```

We can convince ourselves of this result by replicating it many times

```{r}
sim_fun = function() {
n <- 1000
U <- rnorm( n ) # distressing events (unmeasured)
C <- rnorm( n, U ) # religious service attendance, increase with distress
B <- rnorm( n , C + U ) # belief increase with service + distressing events
Y <- rnorm( n , U - C ) # measured distress caused by distress, reduced by church attendance. 
# simulate data
simdat <- data.frame(Belief = B, # belief
  ReligiousService = C, # religious service
  U = U, # distressing events (unmeasured)
  Anxiety = Y)
  sim_s <- lm(Anxiety ~ Belief + ReligiousService, data = simdat)
  sim_s
}

# Replication 1000xs
r_lm = replicate(1000, sim_fun(), simplify = FALSE )

# extract simulations
tab_sim<-purrr::map_dfr(r_lm, broom::tidy)

# extract belief coefficients
mout<-tab_sim %>%
  dplyr::filter(term =="Belief")%>%
  dplyr::mutate_if(is.numeric, round, 5)

# calculate proportion of estimates greater than 0
# all positive
sum(mout$estimate > 0) / length(mout$estimate)

# proportion of belief coefficient p.values < .001
sum(mout$p.value <.001) / length(mout$p.value)

# extract religious service coefficients
tout<-tab_sim %>%
  dplyr::filter(term =="ReligiousService")%>%
  dplyr::mutate_if(is.numeric, round, 5)

# calculate proportion of estimates less than 0
# all negative
sum(tout$estimate < 0) / length(tout$estimate)

# proportion of service coefficient p.values < .001
sum(tout$estimate > 0) / length(tout$estimate)
```

```{r}
parameters::parameters(
  mod1,
  test = "pd",
  priors = FALSE, 
  effects = "all",
  drop = TRUE,
  group_level = FALSE,
  diagnostic = "Rhat") %>%
    mutate_if(is.numeric, ~ round(., 2)) %>%
    mutate_all(funs(str_replace(., "b_", ""))) %>%
    kable(booktabs = T, "latex", caption =  "Simulation reveals how church attendance and belief can deviate where distress increases religious service attendance and belief in God") %>%
    print()
